---
title: "20200703 KA Tracing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(readxl)
library(tidyverse)
library(ggraph)
library(igraph)
library(ggrepel)
setwd("~/Documents/GitHub/tracing")
```

#Import data
```{r}
dat <- read_csv("KAtrace.csv",  skip = 19)
dat$Date <- as.Date(dat$Date, "%d-%b")
```

# Data processing

## Number of daily cases
```{r}
daily <- dat %>% group_by(Date) %>% summarize(Cases = n())
write_csv(daily, "daily_cases.csv")
```


## Classifying biggest clusters
```{r}
dat <- dat %>% group_by(Cluster) %>% mutate(n_cluster = n())
dat %>% group_by(Cluster) %>% summarize(n_cluster = n()) %>% arrange(-n_cluster)
dat$origin <- dat$Cluster
dat$origin <- ifelse(dat$origin < 100, "Others", ifelse(dat$origin == "Influenza like illness", "ILI", ifelse(dat$origin == "Severe Acute Respiratory Infection", "SARI", as.character(dat$Cluster))))

dat$origin_1 <- ifelse(dat$n_cluster < 1000, "Others", as.character(dat$origin))
dat$origin_2 <- ifelse(dat$n_cluster < 1000, "Others", as.character(dat$origin))
```

# Visualizations

## Stacked histogram, date, number and breakdown of cluster
```{r}
dat %>% filter(Cluster != "29-June Trace History Absent" & Cluster != "28-June Trace History Absent" & Cluster != "27-June Trace History Absent") %>% ggplot(aes(Date)) + geom_bar(position = "fill", aes(fill=origin_1), alpha = 0.7, color = "black", size = 0.1) + theme_classic() + theme(legend.position="bottom") + scale_fill_brewer(palette="Dark2", direction = 1) + ggtitle("Distribution of cases diagnosed from various clusters over time") + ylab("Proportion of cases confirmed daily")
ggsave("clusters_stacked.png")
```


```{r, eval = FALSE}
dat %>% filter(Date > "2020-04-01" & Cluster != "29-June Trace History Absent" & Cluster != "28-June Trace History Absent" & Cluster != "27-June Trace History Absent") %>% ggplot(aes(Date)) + geom_bar( aes(fill=origin_2), alpha = 0.7) + theme_light() + theme(legend.position="bottom")+ scale_fill_brewer(palette="Dark2", direction = 1) + ggtitle("Distribution of cases diagnosed from various clusters over time") + ylab("Number of cases confirmed daily")
ggsave("clusters_pct.png")
```

## Distibution of number of people infected by one person

### Data wrangle

#### Up till July 5, how many people have known contact history
```{r}
july5_dat <- dat %>% filter(Date <= "2020-07-05")
july5_known <- july5_dat %>% filter(Cluster != "Unknown")

paste("Of the", nrow(july5_dat), "COVID-19 cases confirmed in Karnataka by July 5,", nrow(july5_known), "or", 100*nrow(july5_known)/nrow(july5_dat),"have a known contact history.")
```

#### Summarize number of cases a given cases was "Parent" (P) of:
```{r}
secondary <- dat %>% filter(Cluster != "Unknown") %>% group_by(P) %>% summarize(`Secondary infections` = n()) 
write_csv(secondary, "secondary_infections.csv")

# Focusing on cases diagnosed till July 5 as parents
july5_parent <- secondary %>% filter(P <= 23474 & P != 0)
```


```{r}
# Mean infections caused by infecting parent
mean_infections <- as.numeric(july5_parent %>% summarise(mean = mean(`Secondary infections`)))

# Number of people with known contacts who caused secondary infections in others with known contacts
nrow(july5_parent)

# Percentage of people with known contacts who caused secondary infections
nrow(july5_parent)/nrow(july5_known)*100

# Number of people with known contacts who caused no secondary infections
nrow(july5_known)-nrow(july5_parent)

100*(nrow(july5_known)-nrow(july5_parent))/nrow(july5_known)
```

#### Distribution of number of infections caused by infecting parent
```{r}
secondary %>% filter(`Secondary infections` < 100) %>% summarize(avg = mean(`Secondary infections`), med = median(`Secondary infections`))
june26_parent %>% filter(`Secondary infections` < 100) %>% ggplot(aes(`Secondary infections`)) + geom_histogram() + geom_vline(aes(xintercept = mean_infections, color = "Mean"), linetype="dashed") + theme_classic() + xlab("Number of infections caused by each patient") + ylab("No. of COVID-19 patients that cause a secondary infection") + ggtitle("Distribution of number of  infections caused")
ggsave("secondary_hist.png")
```


