---
title: "KA Contact Tracing"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
rm(list = ls())
library(readxl)
library(tidyverse)
library(ggraph)
library(igraph)
library(ggrepel)
setwd("~/Documents/GitHub/tracing")
```

```{r, message=FALSE, warning=FALSE}
dat <- read_csv("KAtrace.csv",  skip = 19)
dat$Date <- as.Date(dat$Date, "%d-%b")
```

```{r, echo=FALSE}
## Number of daily cases
daily <- dat %>% group_by(Date) %>% summarize(Cases = n())
write_csv(daily, "daily_cases.csv")
```

# Cleaning & summarizing Clusters variable
```{r}
dat <- dat %>% group_by(Cluster) %>% mutate(n_cluster = n()) #Variable for number of cases in each cluster
cases_per_cluster <- dat %>% group_by(Cluster) %>% summarize(n_cluster = n()) %>% arrange(-n_cluster) #Table for number of cases in each cluster

dat$origin <- ifelse(dat$n_cluster < 20, "Others", ifelse(dat$Cluster == "Influenza like illness", "ILI", ifelse(dat$Cluster == "Severe Acute Respiratory Infection", "SARI", as.character(dat$Cluster)))) #Creating a cleaned up variable with information from `Clusters' for diagramming
```

# Superspreading behaviour 

## How many cases confirmed and contact traced till July 7 caused secondary infections within the next two weeks (till July 21)
```{r}
july7_parent_c <- dat %>% filter(Case <= 26815 & C == 1) # Collapsing C variable
nrow(july7_parent_c)

july7_parent_p <- dat %>% group_by(P) %>% summarize(secondary = n()) %>% filter(P <= 26815 & P != 0) # Collapsing P variable
nrow(july7_parent_p)
```

* Looking at cases that do not overlap in the two approaches
```{r}
setdiff(july7_parent_c$Case, july7_parent_p$P)
setdiff(july7_parent_p$P, july7_parent_c$Case) 
```
* Collapsing on P seems to work better

```{r, echo=FALSE}
write_csv(july7_parent_p, "secondary_infections.csv")
paste(nrow(july7_parent_p), "cases diagnosed and contact traced till July 7 caused secondary infections by July 21, 2020")
```

### How many secondary infections did these 1684 cases cause
```{r}
sum(july7_parent_p$secondary)
```

## How many cases confirmed and contact traced till July 7 did NOT cause secondary infections within the next two weeks (till July 21)

### Subset the data to approximate proportion who were contact traced
I assume that cases fulfilling all of the following criteria were *NOT* contact traced at all:
* Cluster is Unknown 
* Reason is NA
* C = 0
* P = 0  

```{r}
july21_traced <- dat %>% filter(Cluster != "Unknown" | !is.na(Reason) | C != 0 | P != 0)
```

```{r, echo=FALSE}
paste(nrow(july21_traced), "out of", nrow(dat), "cases were contact traced till July 21")
```

* Checking if this makes sense by recalculating number of parents that caused infections by July 5, should be same as above (a lower figure would indicate that I oversubsetted)
```{r}
temp <- july21_traced %>% group_by(P) %>% summarize(secondary = n()) %>% filter(P <= 26815 & P != 0) # Collapsing P variable
nrow(temp) #seems right
```

### Number of cases confirmed by July 7 that did not cause other infections 
```{r}
july21_traced <- dat %>% filter(Case <= 26815)
```


```{r, echo=FALSE}
paste("Of the", nrow(july21_traced), "cases that were confirmed by July 7 and contact traced", nrow(july7_parent_p), "caused secondary infections, while", nrow(july21_traced)-nrow(july7_parent_p), "did not cause any secondary infections at all")
```

## Average number of secondary infections caused by cases that do cause infections
```{r}
mean_infections <- as.numeric(july7_parent_p %>% summarise(mean = mean(secondary)))
july7_parent_p %>% summarize(avg = mean(secondary), med = median(secondary))
july7_parent_p %>% ggplot(aes(secondary)) + geom_histogram() + geom_vline(aes(xintercept = mean_infections, color = "Mean"), linetype="dashed") + theme_classic() + xlab("Number of infections caused by each patient") + ylab("No. of COVID-19 patients that cause a secondary infection") + ggtitle("Distribution of number of  infections caused")
ggsave("secondary_hist.png")
```
# Visualization of change in cluster size over time
```{r}
dat %>% filter(Cluster != "29-June Trace History Absent" & Cluster != "28-June Trace History Absent" & Cluster != "27-June Trace History Absent") %>% ggplot(aes(Date)) + geom_bar(position = "fill", aes(fill=origin), alpha = 0.5, color = "black", size = 0.1) + theme_classic() + theme(legend.position="bottom", legend.spacing = unit(0.4, "points"), legend.text = element_text(size = 6))  + ggtitle("Distribution of cases diagnosed from various clusters over time") + ylab("Proportion of cases confirmed daily")
ggsave("clusters_stacked.png")
```
