---
title: "KA Contact Tracing"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
rm(list = ls())
library(readxl)
library(tidyverse)
library(ggraph)
library(igraph)
library(ggrepel)
setwd("~/Documents/GitHub/tracing")
```

```{r, message=FALSE, warning=FALSE}
dat <- read_csv("KAtrace.csv",  skip = 19)
dat$Date <- as.Date(dat$Date, "%d-%b")
```

```{r, echo=FALSE}
## Number of daily cases
daily <- dat %>% group_by(Date) %>% summarize(Cases = n())
write_csv(daily, "daily_cases.csv")
```

```{r, echo=FALSE}
## Cleaning the "Others" variable, which seems to misclassify some domestic travel cases

dat$Cluster_original <- dat$Cluster
dat$Cluster <- ifelse(grepl("Travel", dat$Reason, fixed = TRUE), "Domestic Travel", ifelse(grepl("Delhi", dat$Reason, fixed = TRUE), "Domestic Travel", ifelse(grepl("travel", dat$Reason, fixed = TRUE), "Domestic Travel", dat$Cluster)))

dat$Cluster <- ifelse(grepl("Indonesia", dat$Reason, fixed = TRUE), "International Travel", ifelse(grepl("Dubai", dat$Reason, fixed = TRUE), "International Travel", ifelse(grepl("London", dat$Reason, fixed = TRUE), "International Travel", ifelse(grepl("Colombo", dat$Reason, fixed = TRUE), "International Travel", ifelse(grepl("Nepal", dat$Reason, fixed = TRUE), "International Travel", ifelse(grepl("Malaysia", dat$Reason, fixed = TRUE), "International Travel", dat$Cluster))))))

o <- dat %>% filter(Cluster == "Others")
o_r <- o %>% group_by(Reason) %>% summarize(n = n()) %>% arrange(-n)
```


```{r, echo=FALSE}
dat <- dat %>% group_by(Cluster) %>% mutate(n_cluster = n()) #Variable for number of cases in each cluster
cases_per_cluster <- dat %>% group_by(Cluster) %>% summarize(n_cluster = n()) %>% arrange(-n_cluster) #Table for number of cases in each cluster

dat$origin <- ifelse(dat$Cluster == "Influenza like illness", "ILI", ifelse(dat$Cluster == "Severe Acute Respiratory Infection", "SARI", ifelse(dat$Cluster == "TJ Congregation from 13th to 18th March in Delhi", "TJ Congregation", ifelse(dat$Cluster == "Pharmaceutical Company in Nanjangud", "Pharma Co, Nanjangud", as.character(dat$Cluster)))))

dat$origin <- ifelse(dat$Cluster == "From Gujarat", "Domestic Travel", ifelse(dat$Cluster == "From Maharashtra", "Domestic Travel", ifelse(dat$Cluster == "From Rajasthan", "Domestic Travel", ifelse(dat$Cluster == "From the Southern States", "Domestic Travel", ifelse(dat$Cluster == "From Middle East", "International Travel",ifelse(dat$Cluster == "From United Kingdom", "International Travel",ifelse(dat$Cluster == "From the rest of Europe", "International Travel", ifelse(dat$Cluster == "From USA", "International Travel", ifelse(dat$Cluster == "From South America", "International Travel",ifelse(dat$Cluster == "Second Generation Contact", "Others", as.character(dat$origin)))))))))))
```

# Superspreading behaviour 

## How many cases confirmed and contact traced till July 7 caused secondary infections within the next two weeks (till July 21)
```{r}
july7_parent_c <- dat %>% filter(Cluster != "Unknown") %>% filter(Case <= 26815 & C == 1) # Collapsing C variable
nrow(july7_parent_c)

july7_parent_p <- dat %>% filter(Cluster != "Unknown") %>% group_by(P) %>% summarize(secondary = n()) %>% filter(P <= 26815 & P != 0 ) # Collapsing P variable
nrow(july7_parent_p)
```

```{r, echo=FALSE}
#* Looking at cases that do not overlap in the two approaches
setdiff(july7_parent_c$Case, july7_parent_p$P) 
setdiff(july7_parent_p$P, july7_parent_c$Case) 
```
* Collapsing on P seems to work better

```{r, echo=FALSE}
temp <- dat %>% ungroup() %>% select(Case, Date)
names(temp) <- c("P", "Date confirmed")
parents <- dat %>% group_by(P) %>% summarize(secondary = n()) %>% filter(P != 0)
secondary <- left_join(parents, temp)
write_csv(secondary, "secondary_infections.csv")
paste(nrow(july7_parent_p), "cases diagnosed and contact traced till July 7 caused secondary infections by July 21, 2020")
```

### How many secondary infections did these 1684 cases cause
```{r}
sum(july7_parent_p$secondary)
```

## How many cases confirmed and contact traced till July 7 did NOT cause secondary infections within the next two weeks (till July 21)

### Subset the data to  proportion who were contact traced (i.e. Cluster is not Unknown)

```{r}
#july21_traced <- dat %>% filter(Cluster != "Unknown" | !is.na(Reason) | C != 0 | P != 0)
july21_traced <- dat %>% filter(Cluster != "Unknown")
```

```{r, echo=FALSE}
paste(nrow(july21_traced), "out of", nrow(dat), "cases were contact traced till July 21")
```


```{r, include=FALSE}
# Checking if this makes sense by recalculating number of parents that caused infections by July 7, should be same as above (a lower figure would indicate that I oversubsetted)
temp <- july21_traced %>% group_by(P) %>% summarize(secondary = n()) %>% filter(P <= 26815 & P != 0) # Collapsing P variable
nrow(temp) #seems right
```
### Total number of secondary infections caused by these cases
```{r}
sum(temp$secondary)
```

### Number of cases confirmed and traced by July 7 that did not cause other infections 
```{r}
july7_traced <- july21_traced %>% filter(Case <= 26815) # Number of cases confirmed and traced by July 7 
nrow(july7_traced)
nrow(july7_parent_p)
nrow(july7_traced)-nrow(july7_parent_p) # Number of cases confirmed and traced by July 7 that did not cause other infections 
```


```{r, echo=FALSE}
paste("Of the", nrow(july7_traced), "cases that were confirmed by July 7 and contact traced", nrow(july7_parent_p), "caused secondary infections, while", nrow(july7_traced)-nrow(july7_parent_p), "did not cause any secondary infections at all")
```

## Average number of secondary infections caused by cases that do cause infections
```{r}
mean_infections <- as.numeric(july7_parent_p %>% summarise(mean = mean(secondary)))
july7_parent_p %>% summarize(avg = mean(secondary), med = median(secondary))

july7_parent_p %>% ggplot(aes(secondary)) + geom_histogram(boundary = 0, alpha = 0.8, fill = "#1a71a3") + geom_vline(aes(xintercept = mean_infections), , color = "Black", linetype="dashed") + theme_minimal() + xlab("Number of Secondary Infections Caused by Each Patient") + ylab("No. of Patients That Cause A Secondary Infection") + ggtitle("Distribution of Number of Secondary Infections Caused By COVID-19 Patients")  + scale_x_continuous(breaks = seq(0, 60,5), labels = seq(0,60, 5))

ggsave("secondary_hist.png")
```
# Number of cases that caused more than 10  secondary infections
```{r}
x <- july7_parent_p %>% filter(secondary > 10)
paste(nrow(x), "cases caused 10 or more secondary infections")
```

# % of cases with unknown P
## March 9 - May 1
```{r}
p <- dat %>% filter(Date < "2020-05-01") %>% group_by(P) %>% summarize(secondary = n()) # number of secondary infections 
x <- dat %>% filter(Date < "2020-05-01") %>% ungroup() %>% summarize(n = n()) # total cases
```

```{r,echo=FALSE}
paste("Out of", as.numeric(x), "cases confirmed by June 1,", p$secondary[1], "(",100*p$secondary[1]/as.numeric(x),")", "had no known parent")
```

## till July 21
```{r}
p <- dat %>% group_by(P) %>% summarize(secondary = n()) # number of secondary infections 
x <- dat %>% ungroup() %>% summarize(n = n()) # total cases
```

```{r,echo=FALSE}
paste("Out of", as.numeric(x), "cases confirmed by June 1,", p$secondary[1], "(",100*p$secondary[1]/as.numeric(x),")", "had no known parent")
```

## Collapsing and making a graph
```{r}
unknown_p <- dat %>% filter(!is.na(P))
unknown_p$known_p <- ifelse(unknown_p$P == 0, 0, 1)
unknown_p <- unknown_p %>% ungroup() %>% mutate(knowns = cumsum(known_p)) %>% select(Case, Date, knowns) 
unknown_p <- unknown_p %>% filter(Date > "2020-03-10") %>% group_by(Date) %>% filter(row_number()==n()) %>% filter(!is.na(Date))
unknown_p$known_parent <- 100*unknown_p$knowns/unknown_p$Case

ggplot(unknown_p, aes(x = Date, y = known_parent)) + geom_line() + theme_minimal() + ggtitle("Percentage of Total Cases With Known Source of Infection Has Been Declining") + ylab("% of Cases With Known Source of Infection")
ggsave("known_transmitter.png")
```
# % of cases were "contact under tracing"
```{r}
may <- dat %>% filter(Date < "2020-05-01") %>% group_by(Cluster) %>% summarize(number = n()) 
x <- dat %>% filter(Date < "2020-05-01") %>% ungroup() %>% summarize(n = n())
100*63/563

total <- dat %>% group_by(Cluster) %>% summarize(number = n())
x <- dat %>% ungroup() %>% summarize(n = n())
100*34100/x[1]
```

# Visualization of change in cluster size over time
```{r}
dat %>% filter(Cluster != "29-June Trace History Absent" & Cluster != "28-June Trace History Absent" & Cluster != "27-June Trace History Absent" & Cluster != "Second Generation Contact Absent" & Cluster != "Domestic Travel History Absent" & Cluster != "International Travel History Absent") %>% ggplot(aes(Date)) + geom_bar(position = "fill", aes(fill=origin), alpha = 1, color = "black", size = 0.05)  + scale_fill_brewer(palette = "Spectral") + theme_minimal() + theme(legend.position="bottom", legend.spacing = unit(0.4, "points"), legend.text = element_text(size = 8), legend.title = element_blank())  + ggtitle("Distribution of Case Origins in Karnataka, March 9 - July 21, 2020") + ylab("Proportion Of Cases Confirmed Daily")
ggsave("clusters_stacked.png")
```
